---
title: "BBets Project"
author: "Alexandra Shields-Knox"
date: "03/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The question is how much money is won/lost on a bet that at least two people have the same b'day in a class of 35.  Instructor wagers 2:1 

Instuctor has done this 15 times,  
1.what is his expected win/loss amount,  
2. how much would the instructor have to wager to make the bet fair 
3. how many students would have to be in the class for a 2:1 bet to be fair?   
 
 
```{r}
days = 1:365

nStudents = 35

nBets = nStudents*15

saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:nBets){
    sampleClass = sample(days, nStudents, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == nStudents) bank = bank - 2
    else bank = bank + 1
  }
saveArray[k]= bank
}

```
 
histogram of bank amounts.   

```{r}
hist(saveArray)
```

Answer questions #1

```{r}
print('average amt:')
print(mean(saveArray))
```

  The average amount of money lost is $230
  
  The amount of money that Dr. J should have to pay is $4.28
  
  The number of students for breakeven at 2:1 is 29 students.